%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{CSR Lead \& Corporate Communication Specialist} % Job Title
{Econocom International Italia} % Company
{Milan, Italy} % Location
{Jun 2026 - Present} % Date(s)
{
\begin{cvitems}
\item Championed \textbf{CSR strategy development} and corporate social responsibility program execution, aligning initiatives with business transformation and sustainability goals.
\item Led \textbf{stakeholder engagement} for CSR initiatives, building partnerships across internal teams and external organizations to drive measurable impact.
\item Directed communication and messaging for \textbf{transformation projects}, ensuring clarity and alignment across organizational levels.
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Marketing \& Communication Specialist} % Job Title
{Econocom International Italia} % Company
{Milan, Italy} % Location
{Dec 2024 - Jun 2026} % Date(s)
{
\begin{cvitems}
\item Directed collaboration across \textbf{internal teams}, channel partners, and the external PR agency, ensuring consistent messaging and timely execution of initiatives.
\item Built and managed the company's \textbf{LinkedIn presence}, defining editorial plans and campaign optimization cycles to strengthen engagement and brand visibility.
\item Led \textbf{project review governance} with \textbf{C-level stakeholders}, delivering structured reports and summaries that improved cross-department priority alignment.
\item Produced \textbf{success case studies} and internal reports used by leadership to communicate achievements and reinforce stakeholder trust.
\item Managed \textbf{budget and resource allocation}, improving execution efficiency across communication activities.
\item Supported \textbf{CSR and transformation projects} through integrated communication and marketing strategy development.
\item Tracked campaign and channel performance through dashboards, enabling faster \textbf{data-driven decisions} and continuous optimization.
\end{cvitems}
}


%---------------------------------------------------------
\cventry
{Marketing \& Communication Specialist} % Job title
{CBA Law Firm} % Organization
{Milan, Italy} % Location
{Apr 2024 - Nov 2024} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item Led the firm’s \textbf{rebranding project}, coordinating creative, content, and digital teams to deliver a unified brand identity across all communication channels.
\item Redesigned \textbf{internal communication workflows} by implementing MailUP and standardized processes, improving communication consistency and execution speed.
\item Managed coordination with media partners and agencies to ensure message alignment and on-time delivery of strategic content.
\item Optimized digital communication strategy through continuous performance tracking, contributing to a \textbf{20\% increase in engagement} in the first quarter.
\item Directed the firm’s \textbf{website migration} from Drupal to WordPress, improving user experience and reducing content management complexity.
\item Planned and delivered corporate and client \textbf{events} that strengthened stakeholder engagement and team cohesion.
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Internal \& Corporate Communication Specialist} % Job title
{Roche S.p.A.} % Organization
{Milan, Italy} % Location
{Jun 2022 - Nov 2023} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item Managed \textbf{internal communication} for over \textbf{500 employees}, ensuring timely information flow and alignment across departments.
\item Coordinated cross-functional teams (IT, creative, and business units) for the launch of the new corporate website, delivering milestones on schedule and maintaining stakeholder alignment.
\item Produced \textbf{management reporting and documentation} for communication initiatives, enabling performance tracking and more informed decision-making.
\item Planned and executed \textbf{10+ corporate events}, overseeing logistics, communication, and budgets while ensuring high operational quality.
\item Monitored media sentiment and reputational risk indicators through analytical tools, providing actionable insights to senior stakeholders.
\item Partnered with creative and media agencies on internal and external campaigns to ensure message consistency and operational excellence.
\end{cvitems}
}

\end{cventries}
