\cvsection{Experience}

\begin{cventries}

%---------------------------------------------------------
\cventry
{CSR Lead \& Corporate Communication Specialist} % Job Title
{Econocom Lease Solution spa} % Company
{Milan, Italy} % Location
{Jun 2026 - Present} % Date(s)
{
\begin{cvitems}
\item Championed \textbf{CSR strategy development} and corporate social responsibility program execution, aligning initiatives with business transformation and sustainability goals.
\item Led \textbf{stakeholder engagement} for CSR initiatives, building partnerships across internal teams and external organizations to drive measurable impact.
\item Directed communication and messaging for \textbf{transformation projects}, ensuring clarity and alignment across organizational levels.
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Marketing \& Communication Specialist} % Job Title
{Econocom Lease Solution spa} % Company
{Milan, Italy} % Location
{Dec 2024 - Jun 2026} % Date(s)
{
\begin{cvitems}
\item Directed collaboration across \textbf{internal teams}, channel partners, and the external PR agency, ensuring consistent messaging and timely execution.
\item Built and managed the company's \textbf{LinkedIn presence}, defining editorial plans and campaign optimization cycles.
\item Led \textbf{project review governance} with \textbf{C-level stakeholders}, delivering structured reports that improved cross-department priority alignment.
\item Produced \textbf{success case studies} and internal reports used by leadership to communicate achievements.
\item Managed \textbf{budget and resource allocation}, improving execution efficiency across communication activities.
\item Tracked campaign and channel performance through dashboards, enabling faster \textbf{data-driven decisions}.
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Marketing \& Communication Specialist} % Job Title
{CBA Law Firm} % Company
{Milan, Italy} % Location
{Apr 2024 - Nov 2024} % Date(s)
{
\begin{cvitems}
\item Led the firm's \textbf{rebranding project}, coordinating creative, content, and digital teams to deliver a unified brand identity.
\item Redesigned \textbf{internal communication workflows} with MailUP and standardized processes, improving consistency and speed.
\item Optimized digital communication strategy through continuous performance tracking, achieving a \textbf{+20\% increase in engagement} in Q1.
\item Directed the firm's \textbf{website migration} from Drupal to WordPress, improving UX and reducing management complexity.
\item Planned and delivered corporate and client \textbf{events} that strengthened stakeholder engagement.
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Internal \& Corporate Communication Specialist} % Job Title
{Roche S.p.A.} % Company
{Milan, Italy} % Location
{Jun 2022 - Nov 2023} % Date(s)
{
\begin{cvitems}
\item Managed \textbf{internal communication} for over \textbf{500 employees}, ensuring timely information flow across departments.
\item Coordinated cross-functional teams (IT, creative, business) for the launch of the new corporate website.
\item Planned and executed \textbf{10+ corporate events}, overseeing logistics, communication, and budgets.
\item Monitored media sentiment and reputational risk indicators, providing actionable insights to senior stakeholders.
\end{cvitems}
}

\end{cventries}
